\setcounter{page}{1}

\section{Introduction}
\hspace{\parindent}Von Neumann and Morgenstern have developed a very fruitful theory of two-person zero-sum games in their book \emph{Theory of Games and Economic Behavior} \cite{1}. This books also contains a theory of $n$-person games of a type which we would call cooperative. This theory is based on an analysis of the interrelationships of the various coalitions which can be formed by the players of the game.

Our theory, in contradistinction, is based on the \emph{absence} of coalitions in that it is assumed that each participant acts independently, without collaboration or communication with any of the others.

The notion of an \emph{equilibrium} point is the basic ingredient in our theory. This notion yields a generalization of the concept of the solution of a two-person zero-sum game. It turns out that the set of equilibrium points of a two-person zero-sum game is simply the set of all pairs of opposing ``good strategies''.

In the immediately following sections we shall define equilibrium points and prove that a finite non-cooperative game always has at least one equilibrium point. We shall also introduce the notions of solvability and strong solvability of a non-cooperative game and prove a theorem on the geometrical structure of the set of equilibrium points of a solvable game.

As an example of the application of our theory we include a solution of a simplified three person poker game.

The motivation and interpretation of the mathematical concepts employed in the theory are reserved for discussion on a special section of this paper.

\thispagestyle{empty}
\clearpage

\newpage
\setcounter{page}{2}
\section{Formal Definitions and Terminology}
\hspace{\parindent}In this section we define the basic concepts of this paper and set up standard terminology and notation. Important definitions will be preceeded by a subtitle indicating the concept defined\footnote{We actually use \textbf{boldface} for definitions instead, but this note on the subtitles is left in to preserve the wording of the original.}. The non-cooperative idea will be implicit, rather than explicit, below.
\begin{definition}[Finite Game]
    For us an $\mathbf n$\textbf{-person game} will be a set of $n$ \textbf{players}, or \textbf{positions}, each with an associated finite of \textbf{pure strategies}; and corresponding to each player, $i$, a \textbf{pay-off function}, $P_i $, which maps the set of all $n$-tuples of pure strategies into the real numberes. When we use the word $\mathbf n$\textbf{-tuples} we shall always mean a set of $n$ items, with each item associated with a different player.
\end{definition}
\begin{definition}[Mixed Strategy, $S_i $]
   A \textbf{mixed strategy} of player $i$ will be a collection of non-negative numbers which have unit sum and are in one to one correspondence with his pure strategies.
\end{definition}
   We write $s_i=\sum_{\alpha }^{} c_{i\alpha }\pi_{i\alpha } $ with $\sum_{\alpha }^{} c_{i\alpha }=1 $ and $c_{i\alpha }\geq 0$ to represent such a mixed strategy, where the $\pi_{i\alpha }$'s are the pure strategies of player $i$. We regard the $s_i $'s as points in a simplex whose vertices are the $\pi_{i\alpha }$'s. This simplex may be regarded as a convex subset of a real vector space, giving us a natural process of linear combination for the mixed strategies.

   We shall use the suffixes $i,j,k$ for players and $\alpha ,\beta ,\gamma $ to indicate various pure strategies of a player. The symbols $s_i ,t_i ,$ and $v_i $, etc.\ will indicate mixed strategies; $\pi_{i\alpha }$ will indicate the $i$th player's $\alpha $th pure strategy, etc.

   \begin{definition}[Pay-off functions, $P_i $]
       The pay-off function, $P_i $, used in the definition of a finite game above, has a unique extension to the $n$-tuples of mixed strategies which is linear in the mixed strategy of each player [$n$-linear]. This extension we shall also denote $P_i $, writing $P_i (s_1,s_2,\cdots ,s_n )$.
   \end{definition}
   We shall write $\mathcal{s} $ or $\mathcal{t} $ to denote an $n$-tuble of mixed strategies and if $\mathcal{s} =(s_1,\cdots ,s_n )$ then $P_i (\mathcal{s} )$ shall mean $P_i (s_1,s_2,\cdots ,s_n )$. Such an $n$-tuple, $\mathcal{s} $, will also be regarded as as point in a vector space, which space could be obtained by multiplying together the vector spaces containing the mixed strategies. And the set of all such $n$-tuples forms, of course, a convex polytope, the product of the simplices representing the mixed strategies.

   For convenience we introduce the substitution notation $(\mathcal{s} ;\mathcal{t} _i )$ to stand for $(s_1,s_2,\cdots ,s_{i-1}, t_i ,s_{i+1},\cdots ,s_n )$ where $\mathcal{s} =(s_1,s_2,\cdots ,s_n )$. The effect of successive substitutions $((\mathcal{s} _i ;t_i );v_j )$ we indicate by $(\mathcal{s} ;t_i ;v_j )$, etc.
   \begin{definition}[Equilibrium Points]
      An $n$-tuple $\mathcal{s} $ is an \textbf{equilibrium point} if and only if for every $i$ 
      \begin{equation}\label{eqpt}
          P_i (\mathcal{s} )= \underset{\text{all} \, v_i \text{'s} }{\operatorname{max}}\left[ P_i (\mathcal{s} ;v_i ) \right] .
      \end{equation}
\thispagestyle{empty}
      Thus an equilbrium point is an $n$-tuple $\mathcal{s} $ such that each player's mixed strategy maximizes his pay-off if the strategies of the others are held fixed. Thus each player's strategy is optimal against those of the others. We shall occasionally abbreviate equilibrium point by eq.\ pt.
   \end{definition}
   We say that a mixed strategy $s_i $ \textbf{uses} a pure strategy $\pi_{i\beta }$ if $s_i=\sum_{\alpha }^{} c_{i\alpha }\pi_{i\alpha }$ and $c_{i\beta }>0$. If $\mathcal{s} =(s_1,s_2,\cdots ,s_n )$ and $s_i $ uses $\pi_{i\alpha }$ we also say that $\mathcal{s} $ uses $\pi_{i\alpha }$.

   From the linearity of $P_i (s_1,\cdots ,s_n )$ in $S_i $, 
   \begin{equation}
       \underset{\text{all} \, v_i \text{'s} }{\operatorname{max}} \left[ P_i (\mathcal{s} ;v_i ) \right] = \underset{\alpha }{\operatorname{max}} \left[ P_i (\mathcal{s} ;\pi_{i\alpha }) \right] .
   \end{equation}
   We define $P_{i\alpha }(\mathcal{s} )=P_i (\mathcal{s} ;\pi_{i\alpha })$. Then we obtain the following trivial necessary and sufficient condition for $\mathcal{s} $ to be an equilibrium point: 
   \begin{equation}\label{equib}
       P_i (\mathcal{s} )= \underset{\alpha }{\operatorname{max}} \, P_{i\alpha }(\mathcal{s} ).
   \end{equation}
   If $\mathcal{s} =(s_1,s_2,\cdots ,s_n )$ and $s_i =\sum_{\alpha }^{} c_{i\alpha }\pi_{i\alpha }$ then $P_i (\mathcal{s} )=\sum_{\alpha }^{} c_{i\alpha }P_{i\alpha }(\mathcal{s} )$, consequently for \eqref{equib} to hold we must have $c_{i\alpha }=0$ whenever $P_{i\alpha }(\mathcal{s} )< \underset{\beta }{\operatorname{max}} \, P_{i\alpha }(\mathcal{s} )  $, which is to say that $\mathcal{s} $ does not use $\pi_{i\alpha }$ unless it is an optimal pure strategy for player $i$. So we write 
   \begin{equation}\label{suf}
       \text{if} \ \pi_{i\alpha } \ \text{is used in} \ \mathcal{s} \ \text{then} \ P_{i\alpha }(\mathcal{s} )=\underset{\beta }{\operatorname{max}} \, P_{i\beta }(\mathcal{s} )
   \end{equation}
   as another necessary and sufficient condition for an equilibrium point.

   Since a criterion \eqref{equib} for an eq. pt. can be expressed as the equating of two continuous functions on the space of $n$-tubles $\mathcal{s} $ the eq. pts. obviously form a closed subset of this space. Actually, this subset is formed from a number of pieces of algebraic varieties, cut out by other algebraic varieties.

   \section{Existence of Equilibrium Points}
   I have previously published in [Proc.\ N.\ A.\ S.\ 36 (1950) 48-49] \cite{2} a proof of the result below based on Kakutani's generalized fixed point theorem. The proof given here uses the Brouwer theorem.

   The method is to set up a sequence of continuous mappings: $\mathcal{s} \to \mathcal{s} '(\mathcal{s} ,1);\ \mathcal{s} \to \mathcal{s} '(\mathcal{s} ,2); \cdots $ whose fixed points have an equilibrium point as a limit points. A limit mapping exists, but is discontinuous, and need not have any fixed points.
\begin{theorem}
    Every finite game has an equilibrium point.
\end{theorem}
\begin{proof}
    Using our standard notation, let $\mathcal{s} $ be an $n$-tuple of mixed strategies, and $P_{i\alpha }(\mathcal{s} )$ the pay-off to player $i$ if he uses his pure strategy $\pi_{i\alpha }$ and the others use their respective mixed strategies in $\mathcal{s} $. For each integer $\lambda$ we define the following continuous functions of $\mathcal{s} $: 
    \begin{gather*}
        q_i (\mathcal{s} )= \underset{\alpha }{\operatorname{max}} \, P_{i\alpha }(\mathcal{s} ), \\
        \phi_{i\alpha }(\mathcal{s} ,\lambda )= P_{i\alpha }(\mathcal{s}) -q_i (\mathcal{s} )+ \frac{1}{\lambda}, \ \text{and} \\
        \phi_{i\alpha }^+ (\mathcal{s} ,\lambda)=\operatorname{max}\left[ 0,\phi_{i\alpha }(\mathcal{s} ,\lambda) \right] .
    \end{gather*}
    Now $\sum_{\alpha }^{} \phi_{i\alpha }^+ (\mathcal{s} ,\lambda)\geq \underset{\alpha }{\max} \, \phi_{i\alpha }^+(\mathcal{s} ,\lambda)=\frac{1}{\lambda}>0$ so that $c_{i\alpha }'(\mathcal{s} ,\lambda)= \frac{\phi_{i\alpha }^+ (\mathcal{s} ,\lambda)}{\sum_{\beta }^{} \phi_{i\beta }^+(\mathcal{s} ,\lambda)}$ is continuous. Define $s'_i (\mathcal{s} ,\lambda)=\sum_{\alpha }^{} \pi_{i\alpha }c'_{i\alpha }(\mathcal{s} ,\lambda)$ and $\mathcal{s} '(\mathcal{s} ,\lambda)=(s_1',s_2',\cdots ,s_n ')$. Since all the operations have preserved continuity, the mapping $\mathcal{s} \to \mathcal{s} '(\mathcal{s} ,\lambda)$ is continuous; and since the space of $n$-tuples, $\mathcal{s} $, is a cell, there must be a fixed point for each $\lambda$. Hence there will be a subsequence  $\lambda_{\mu}$, converging to $\mathcal{s} ^*$, where $\mathcal{s} _{\mu}$ is fixed under the mapping $\mathcal{s} \to \mathcal{s} '(\mathcal{s} ,\lambda _{(\mu)})$. 

    Now supposed $\mathcal{s} ^*$ were not an equilibrium point. Then if $\mathcal{s} ^*=(s_1^*,\cdots ,s_n ^*)$ some component $s_i ^*$ must be non-optimal against the others, which means $s_i ^*$ uses some pure strategy $\pi_{i\alpha }$ which is non-optimal [see \eqref{suf}]. This means that $P_{i\alpha }(\mathcal{s} ^*)<q_i (\mathcal{s} ^*)$ which justifies writing $P_{i\alpha }(\mathcal{s} ^*)-q_i (\mathcal{s} ^*)<-\epsilon$.

    From continuity, if $\mu$ is large enough,
    \[
        \Big| \left[ P_{i\alpha }(\mathcal{s} _{\mu}) -q_i (\mathcal{s} _{\mu})\right] -\left[ P_{i\alpha }(\mathcal{s} ^*)-q_i (\mathcal{s} ^*) \right] \Big| < \frac{\epsilon}{2} \quad \text{and} \quad \frac{1}{\lambda _{(\mu)}}< \frac{\epsilon }{2}.
    \] Adding, $P_{i\alpha }(\mathcal{s} _{\mu})-q_i (\mathcal{s} _{\mu})+\frac{1}{\lambda_{(\mu)}}<0$ which is simply $\phi_{i\alpha }(\mathcal{s} _{\mu},\lambda_{(\mu)})<0$, whence $\phi_{i\alpha }^+(\mathcal{s} _{\mu},\lambda_{(\mu)})=0$, whence $c_{i\alpha }'(\mathcal{s} _{\mu},\lambda_{(\mu)})=0$. From this last equation we know that $\pi_{i\alpha }$ is not used in $\mathcal{s} _{\mu}$ since $\mathcal{s} _{\mu}=\sum_{\alpha }^{} \pi_{i\alpha }c_{i\alpha }'(\mathcal{s} _{\mu},\lambda_{(\mu)})$, because $\mathcal{s} _{\mu}$ is a fixed point.

    And since $\mathcal{s} _{\mu}\to \mathcal{s} ^*$, $\pi_{i\alpha }$ is not used in $\mathcal{s} ^*$, which contradicts our assumption. Hence $\mathcal{s} ^*$ is indeed an equilibrium point.
\end{proof}
\section{Symmetries of Games}
\hspace{\parindent}An \textbf{automorphism}, or \textbf{symmetry}, of a game will be a permutation of its pure strategies which satisfies certain conditions, given below.

If two strategies belong to a single player they must go into two strategies belonging to a single player. Thus if $\phi$ is the permutation of the pure strategies it induces a permutation $\psi$ of the players. 

Each $n$-tuple of pure strategies is therefore permuted into another $n$-tuple of pure strategies. We may call $\chi$ the induced permutation of these $n$-tupless. Let $\xi$ denote an $n$-tuple of pure strategies and $P_i (\xi)$ the pay-off to player $i$ when the $n$-tuple $\xi$ is employed. We require that if \[
    j=i^{\psi} \quad \text{then} \quad P_j (\xi^{\chi})=P_i (\xi)
\] which completes the definition of a symmetry.

The permutation $\phi$ has a unique linear extension to the mixed strategies. If $s_i =\sum_{\alpha }^{} c_{i\alpha }\pi_{i\alpha }$ we define $(s_i )^{\phi}=\sum_{\alpha }^{} c_{i\alpha }(\pi_{i\alpha })^{\phi}.$ The extension of $\phi$ to the mixed strategies clearly generates an extension of $\chi$ to the $n$-tuples of mixed strategies. We shall also denote this by $\chi$.

We define a \textbf{symmetric} $\mathbf n$\textbf{-tuple} $\mathcal{s} $ of a game by $\mathcal{s} ^{\chi}=\mathcal{s} $ for all $\chi$'s, it being understood that $\chi$ means a permutation derived from a symmetry $\phi$.
\begin{theorem}
    Any finite game has a symmetric equilibrium point.
\end{theorem}
\begin{proof}
    First we note that $s_{i0}=\frac{\sum_{\alpha }^{} \pi_{j\alpha }}{\sum_{\alpha }^{} 1}$ has the property $\left( s_{i0} \right) ^{\phi}=s_{j0}$ where $j=i^{\psi}$, so that the $n$-tuple $\mathcal{s}_0=(s_{10},s_{20},\cdots ,s_{n0})$ is fixed under any $\chi$; hence any game has at least one symmetric $n$-tuple. 

    If $\mathcal{s} =(s_1,\cdots ,s_n )$ and $\mathcal{t} =(t_1,\cdots ,t_n )$ are symmetric then $\frac{\mathcal{s} +\mathcal{t} }{2}=\left( \frac{s_1+t_1}{2},\cdots ,\frac{s_n +t_n }{2} \right) $ is so too because $\mathcal{s} ^{\chi}=\mathcal{s} \iff s_j =(s_i )^{\phi}$ where $j=i^{\psi}$, hence \[
            \frac{s_j +t_j }{2}=\frac{(s_i )^{\phi}+(t_i )^{\phi}}{2}=\left( \frac{s_i +t_i }{2} \right) ^{\phi}, \quad \text{hence} \quad \left( \frac{\mathcal{s} +\mathcal{t} }{2} \right) ^{\chi}=\frac{\mathcal{s} +\mathcal{t} }{2}.
    \] This shows that the set of symmetric $n$-tuples is a convex subset of the space of $n$-tuples since it is obviously closed.

    Now observe that for each $\lambda$ the mapping $\mathcal{s} \to \mathcal{s} '(\mathcal{s} , \lambda)$ used in the proof of existence theorem was intrinsically defined. Therefore, if $\mathcal{s}_2=\mathcal{s} '(\mathcal{s} _1,\lambda)$ and $\chi$ is an automorphism of the game we will have $\mathcal{s} _2^{\chi}=\mathcal{s} '(\mathcal{s} _1^{\chi},\lambda)$. If $\mathcal{s} _1$ is symmetric $\mathcal{s} _1=\mathcal{s} _1$ and therefore $\mathcal{s} _2^{\chi}=\mathcal{s} '(\mathcal{s} _1,\lambda)=\mathcal{s} _2$. Consequently this mapping maps the set of symmetric $n$-tuples to itself. 

    Since this set is a cell there must be a symmetric fixed point of $\mathcal{s} _{\lambda}$. And, as in the proof of the existence theorem we could obtain a limit point $\mathcal{s} ^*$ which would have to be symmetric.
\end{proof}
\section{Solutions}
\hspace{\parindent}We define here solutions, strong solutions, and sub-solutions. A non-cooperative game does not always have a solution, but when it does the solution is unique. Strong solutions are solutions with special properties. Sub-solutions always exist and have many of the properties of solutions, but lack uniqueness.

$S_i $ will denote a set of mixed strategies of player $i$ and $\mathcal{S} $ a set of $n$-tuples of mixed strategies. 

\begin{definition}[Solvability]
    A game is solvable if its set, $\mathcal{S} $, of equilibrium points satisfies the condition 
    \begin{equation}\label{solvable}
        (\mathcal{t} ; v_i ) \in \mathcal{S}  \ \text{and}\ \mathcal{s} \in \mathcal{S}  \implies  (\mathcal{s} ; v_i )\in \mathcal{S} \ \text{for all} \ i\text{'s}.
    \end{equation}
\end{definition}
This is called the \textbf{interchangeability} condition. The \textbf{solution} of a solvable game is its set, $\mathcal{S} $, of equilibrium points.
\begin{definition}[Strong Solvability]
    A game is \textbf{strongly solvable} if it has a solution, $\mathcal{S} $, such that for all $i$'s \[
        \mathcal{s} \in \mathcal{S} \ \text{and} \ P_i (\mathcal{s} ;v_i )=P_i (\mathcal{s} )\implies (\mathcal{s} ;v_i )\in \mathcal{S} 
    \] and then $\mathcal{S} $ is called a \textbf{strong solution}.
\end{definition}
\begin{definition}[Equilibrium Strategies]
    In a solvable game set $S_i $ be the set of all mixed strategies $s_i $ such that for some $\mathcal{t} $ the $n$-tuple $(\mathcal{t} ;s_i )$ is an equilibrium point. [$s_i $ is the $i$th component of some equilibrium point.] We call $S_i $ the set of \textbf{equilibrium strategies} of player $i$.
\end{definition}
\begin{definition}[Sub-solutions]
    If $\mathcal{S} $ is a subset of the set of equilibrium points of a game and satisfies condition \eqref{solvable}; and if $\mathcal{S} $ is maximal relative to this property then we call $\mathcal{S} $ a \textbf{sub-solution}. 

For any sub-solution $\mathcal{S} $ we define the $i$th \textbf{factor set}, $S_i $, as the set of all $s_i $'s such that $\mathcal{S} $ contains $(\mathcal{t} ;s_i )$ for some $\mathcal{t} $.
\end{definition}

Note that a sub-solution, when unique, is a solution; and its factor sets are the sets of equilibrium strategies.
\begin{theorem}\label{factor}
    A sub-solution, $\mathcal{S} $, is the set of all $n$-tuples $(s_1,s_2,\cdots ,s_n )$ such that each $s_i \in S_i $ where $S_i $ is the $i$th factor set of $\mathcal{S} $. Geometrically, $\mathcal{S} $ is the product of its factor sets.
\end{theorem}
\begin{proof}
    Consider such an $n$-tuple $(s_1,\cdots ,s_n )$. By definition $\exists \mathcal{t}_1 , \mathcal{t_2} ,\cdots ,\mathcal{t}_n $ such that for each $i \ (\mathcal{t} _i ; s_i )\in \mathcal{S} $. Using the condition \eqref{solvable} $n-1$ times we obtain successively $\mathcal{t_1} ;s_1;s_2)\in \mathcal{S} ,\cdots , (\mathcal{t}_1;s_1;s_2;s_3;\cdots ;s_n )\in \mathcal{S} $ and the last is simply $(s_1,s_2,\cdots ,s_n )\in \mathcal{S} $, which we needed to show.
\end{proof}
\begin{theorem}
    The factor sets $S_1,S_2,\cdots ,S_n $ of a sub-solution are closed and convex as subsets of the mixed strategy space.
\end{theorem}
\begin{proof}
    It suffices to show two things: 
    \begin{enumerate}[label=(\alph*)]
        \item if $s_i $ and $s_i '\in S_i $ then $s_i ^*=(s_i +s_i ')/2 \in S_i $;
        \item if $s_i ^{\#}$ is a limit point of $S_i $ then $s_i ^{\#}\in S_i $.
    \end{enumerate}
 \hspace{\parindent}Let $\mathcal{t} \in \mathcal{S} $. Then we have $P_j (\mathcal{t} ;s_i )\geq P_j (\mathcal{t} ;s_i ;v_j )$ and $P_j (\mathcal{t} ;s_i )\geq P_j (\mathcal{t} ;s_i ';v_j)$ for any $v_j $, by using the criterion of \eqref{eqpt} for an eq. pt. Adding these inequalities, using the linearity of $P_j (s_1,\cdots ,s_n )$ in $S_i $, and dividing by 2, we get $P_j (\mathcal{t} ;s_i ^*)\geq P_j (\mathcal{t} ;s_i ^*;v_j )$ since $s_i ^*= (s_i +s_i ')/2$. From this we know that $(\mathcal{t} ;s_i ^*)$ is an eq. pt. for any $t\in \mathcal{S} $. If the set of all such eq. pts. $(\mathcal{t} ;s_i ^*)$ is added to $\mathcal{S} $ the augmented set clearly satisfies condition \eqref{solvable}, and since $\mathcal{S} $ was to be maximal it follows that $s_i ^*\in S_i $.

 To attack (b) note that the $n$-tuple $(\mathcal{t} ;s_i ^{\#})$, where $\mathcal{t} \in \mathcal{S} $ will be a limit point of the set of $n$-tuples of the form $(\mathcal{t} ; s_i )$ where $s_i \in S_i $, since $s_i ^{\#}$ is a limit point of $S_i $. But this set is a set of eq. pts. and hence any point in its closure is an eq. pt., since the set of all eq. pts. is closed [see pg. 3]. Therefore $(\mathcal{t} ; s_i ^{\#})$ is an eq. pt. and hence $s_i ^{\#}\in S_i $ from the same argument as for $s_i ^*$.
\end{proof}
\begin{definition}[Values]
    Let $\mathcal{S} $ be the set of equilibrium points of a game. We define \[
        v_i ^+ = \underset{\mathcal{s} \in \mathcal{S} }{\max} \left[ P_i (\mathcal{s} ) \right] , \quad v_i ^- = \underset{\mathcal{s} \in \mathcal{S} }{\min} \left[ P_i (\mathcal{s} ) \right] .
    \] If $v_i ^+=v_i ^-$ we write $v_i =v_i ^+=v_i ^-$. $v_i ^+$ is the \textbf{upper value} to player $i$ of the game; $v_i ^-$ the \textbf{lower value}; and $v_i $ the \textbf{value}, if it exists.

Values will obviously have to exist if there is but one equilibrium point.
\end{definition}
One can define \textbf{associated values} for a sub-solution by restricting $\mathcal{S} $ to the eq. pts. in the sub-solution and then using the same defining equations as above. 

A two-person zero-sum game is always solvable in the sense defined above. The sets of equilibrium strategies $S_1 $ and $S_2$ are simply the sets of ``good'' strategies. Such a game is not generally strongly solvable; strong solutions exist only when there is a ``saddle point'' in \emph{pure} strategies.

\section{Geometrical Form of Solutions}
\hspace{\parindent}In the two-person zero-sum case it has been shown that the set of ``good'' strategies of a player is a convex polyhedral subset of his strategy spaces. We shall obtain the same result for a player's set of equilibrium strategies in any solvable game.

\begin{theorem}
    The sets $S_1 ,S_2,\cdots ,S_n $ of equilibrium strategies in a solvable game are polyhedral convex subsets of the respective mixed strategy spaces. 
\end{theorem}
\begin{proof}
    An $n$-tuple $\mathcal{s} $ will be an equilibrium point if and only if for every $i$ 
    \begin{equation}
        P_i (\mathcal{s} ) = \underset{\alpha }{\max} \, P_{i\alpha }(\mathcal{s} )
    \end{equation}
    which is condition \eqref{equib}. An equivalent condition is for every $i$ and $\alpha $ 
    \begin{equation}\label{eqq}
        P_i (\mathcal{s} ) - P_{i\alpha }(\mathcal{s} ) \geq 0.
    \end{equation}
    Let us now consider the form of the set $S_j $ of the equilibrium strategies, $s_j $, of player $j$. Let $\mathcal{t} $ be any equilibrium point, then $(\mathcal{t} ;s_j )$ will be an equilibrium point if and only if $s_j \in S_j $, from Theorem \eqref{factor}. We now apply condition \eqref{eqq} to $(\mathcal{t} ;S_j )$, obtaining
    \begin{equation}
        s_j \in S_j  \iff \text{for all} \ i,\alpha \quad P_i (\mathcal{t} ;s_j )-P_{i\alpha }(\mathcal{t} ;s_j )\geq 0.
    \end{equation}
    Since $P_i $ is $n$-linear and $\mathcal{t} $ is constant these are a set of linear inequalities of the form $F_{i\alpha }(s_j )\geq 0$. Each such inequality is either satisfied for all $s_j $ or for those lying on and to one side of some hyperplane passing through the strategy simplex. Therefore, the complete set [which is finite] of conditions will all be satisfied simultaneously on some convex polyhedral subset of player $j$'s strategy simplex. [Intersection of half-spaces.]

    As a corollary we may conclude that $S_k $ is the convex closure of a finite set of mixed strategies [vertices].
\end{proof}
\section*{Simple Examples}
\hspace{\parindent}These are intended to illustrate the concepts defined in the paper and display special phenomena which occur in the game.

The first player has the roman letter strategies and the pay-off to the left, etc.
\begin{example}
    \,
                \begin{figure}[htbp]
  \begin{minipage}[c]{0.25\linewidth}
      \!\!\!
    \begin{tabular}{cccc}
        5 &   $a$ &  $\alpha $ & -3 \\
        -4 & $a$ & $\beta $ & 10\\
        -5 & $b$ & $\alpha $ &5\\
        3 & $b$ & $\beta $ &-4
    \end{tabular}
  \end{minipage}
  \begin{minipage}[c]{0.65\linewidth}
      \centering\text{Weak Solutions: $\left( \frac{9}{16}a+\frac{7}{16}b, \frac{7}{17}\alpha +\frac{10}{17}\beta \right) $.}\vspace{0.2cm}\newline\text{$\ v_1=-\frac{5}{17}, \ v_2=+\frac{1}{2}$}
  \end{minipage}
\end{figure}
\end{example}
\begin{example}
    \,
                \begin{figure}[htbp]
  \begin{minipage}[c]{0.25\linewidth}
      \!\!\!
    \begin{tabular}{cccc}
        1 &   $a$ &  $\alpha $ & 1 \\
        -10 & $a$ & $\beta $ & 10\\
       10 & $b$ & $\alpha $ &-10\\
        -1 & $b$ & $\beta $ &-1
    \end{tabular}
  \end{minipage}
  \begin{minipage}[c]{0.65\linewidth}
     \centering \text{Strong Solution: $(b,\beta) $.}\vspace{0.2cm}\newline\text{$v_1=v_2=-1$}
  \end{minipage}
\end{figure}
\end{example}
\begin{example}
    \,
                \begin{figure}[htbp]
  \begin{minipage}[c]{0.25\linewidth}
      \!\!\!
    \begin{tabular}{cccc}
        1 &   $a$ &  $\alpha $ & 1 \\
        -10 & $a$ & $\beta $ & 10\\
       10 & $b$ & $\alpha $ &-10\\
        -1 & $b$ & $\beta $ &-1
    \end{tabular}
  \end{minipage}
  \begin{minipage}[c]{0.65\linewidth}
     \centering \text{Strong Solution: $(b,\beta) $.}\vspace{0.2cm}\newline\text{$v_1=v_2=-1$}
  \end{minipage}
\end{figure}
\end{example}
